A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-30 main.tex
Writing CSP.

% run

% CSP

>>>>

% transition-related symbols disappears when the empty transition is substituted.

Another important rule about a transition variable is 
that a transition variable related symbol disappears when the empty transition is substituted to the transition variable.
For example, $(\TB_\epsilon (\lambda x:\I.x))$ is equivalent to $(\lambda x:\I.x)$.
This rule is applied all transition variable related symbols: $\TB_\alpha, \TBL_\alpha$, and $\%_\alpha$.

% run
The main purpose of transition abstractions and transition applications are to represent {\bf{run}} operator.
In multistage calculus, {\bf{run}} is a very important operator.
It changes quoted code to the original code.
{\bf{run}} is realized with application of the empty transition $\epsilon$.
For example, $\Lambda\alpha.(\TB_\alpha (\lambda x:\I.x))\ \epsilon$ becomes $\lambda x:\I.x$
because $\TB_\epsilon$ is disappeared.

% CSP
CSP, cross-stage persistence is an important feature of multistage calculus.
\red{It enable us to embed value at an outer transition into an inner transition}.
